High performance computing for global optimization problems

### 2017-11-09 2018/ITNT/ITNT2018.tex
computations -> computing

The organization of the parallel computations with the use of the recursive 
optimization scheme has been considered in details for the shared/distributed 
memory as well as for the accelerators in \cite{Sysoyev,BarkalovLebedev}. However, in these works the 
problems were considered, in which the time of the trial execution didn’t 
depend on the trial point. Here, the problem is considered assuming that in 
the function $\varphi(y_1,...,y_N)$ it is possible to select more difficult 
part $f(y_1,...,y_N)$ (depending on all problem parameters) and a simpler 
part $g(y_s,...,y_N )$ (depending on a part of the parameters only), for 
example, $\varphi(y)= f(y)g(y)$.

>>>>

The organization of parallel computing with the use of the recursive 
optimization scheme has been considered in details for the shared/distributed 
memory as well as for the accelerators in \cite{Sysoyev,BarkalovLebedev}. However, in these works the 
problems were considered, in which the time of the trial execution didn’t 
depend on the trial point. Here, the problem is considered assuming that in 
the function $\varphi(y_1,...,y_N)$ it is possible to select more difficult 
part $f(y_1,...,y_N)$ (depending on all problem parameters) and a simpler 
part $g(y_s,...,y_N )$ (depending on a part of the parameters only), for 
example, $\varphi(y)= f(y)g(y)$.
